Supplementary Figure 1a

### 2017-12-03 inst/cellular_localization_encode/cellular_localization_encode.Rmd
done adding the TCGA correlation TABLE, more work on manuscript (citations)

packages <- c(
    "tidyverse",
    "printr",
    "ggthemes",
    "readr",
    "miR34AasRNAproject",
    "grid",
    "gtable"
)
purrr::walk(packages, library, character.only = TRUE)
rm(packages)

>>>>

packages <- c(
    "tidyverse",
    "printr",
    "ggthemes",
    "miR34AasRNAproject",
    "grid",
    "gtable"
)
purrr::walk(packages, library, character.only = TRUE)
rm(packages)

### 2017-12-03 inst/stable_line_expression/stable_line_expression.Rmd
re-ran all rmds and added sessionInfo to all
done adding the TCGA correlation TABLE, more work on manuscript (citations)

n <- data.frame(
  name = c(
    "PC3 mock",
    "PC3 miR34a asRNA",
    "Skov3 mock",
    "Skov3 miR34a asRNA",
    "Saos2 mock",
    "Saos2 miR34a asRNA"
  ),
  n = c(3, 5, 4, 4, 5, 5)
)
n

>>>>

n <- data.frame(
  name = c(
    "PC3 mock",
    "PC3 miR34a asRNA",
    "Skov3 mock",
    "Skov3 miR34a asRNA",
    "Saos2 mock",
    "Saos2 miR34a asRNA"
  ),
  n = c(5, 5, 4, 4, 5, 5)
)
n

### 2017-12-03 inst/tcga_correlation/tcga_correlation.Rmd
fixing headers in Rmds
re-ran all rmds and added sessionInfo to all
done adding the TCGA correlation TABLE, more work on manuscript (citations)

####_Introduction_

@@

####_Results_

@@

Insert code here from Erik and write Intro Methods etc

```{r, out.width = "1000px"}

url <- fileMap(type = "png")["figure1c"][[1]]
knitr::include_graphics(file.path(projectUrl, url))

@@

####_Conclusions_

>>>>

#### _Introduction_
We interogated RNA sequencing data from TCGA to determine in miR34a and miR34a asRNA expression was correlated in both TP53 wild type and mutated samples.

@@

#### _Results_
```{r}
url <- fileMap(type = "rds")["figure1c"][[1]]
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

#normalize expression values
data <- mutate(
    data,
    RP3 = log2(RP3 / max(RP3)),
    miR34a = log2(miR34a / max(miR34a))  
  )

#add BRCA subtypes
data <- data %>%
  mutate(PAM50 = if_else(is.na(PAM50), "", PAM50)) %>%
  mutate(cancer_PAM50 = gsub("BRCA", "BRCA ", paste(cancer, PAM50, sep = "")))

#sort 
data <- arrange(data, cancer_PAM50, TP53, RP3)

#remove infinite data
data <- filter(data, !is.infinite(RP3) & !is.infinite(miR34a))

#diploid only
data <- filter(data, abs(RP3_cna) < 0.1)
```

```{r, fig.align='center', fig.height=8, fig.width=12, message = FALSE}
#plot
plotTCGAcorrelation(data, type = "diploid only")

#save to pdf
# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure1c"][[1]])
# pdf(path, width = 28)
# data %>%
#   arrange(cancer_PAM50, TP53, RP3) %>%
#   plotTCGAcorrelation(type = "diploid only")
# invisible(dev.off())
```

@@

@@

#### _Conclusions_
miR34a asRNA and miR34a tend to be highly correlated in the cancer types examined in both TP53 wild type and mutated samples. In addition, the results indicate that both miR34a asRNA and miR34a expression levels are decreased in the presence of TP53 mutations.

### 2017-12-03 inst/tcga_correlation_table/tcga_correlation_table.Rmd
adding tcga_correlation_table as .rds
ran tcga correlation table .rmd after last 2 commits
re-ran all rmds and added sessionInfo to all
done adding the TCGA correlation TABLE, more work on manuscript (citations)

```{r, out.width = "850px"}

url <- fileMap(type = "png")["suppFigure1a"][[1]]
knitr::include_graphics(file.path(projectUrl, url))

>>>>

```{r, warning = FALSE}
url <- fileMap(type = "rds")["figure1c"][[1]]
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

#normalize expression values
data <- mutate(
    data,
    RP3 = log2(RP3 / max(RP3)),
    miR34a = log2(miR34a / max(miR34a))  
  )

#add BRCA subtypes
data <- data %>%
  mutate(PAM50 = if_else(is.na(PAM50), "", PAM50)) %>%
  mutate(cancer_PAM50 = gsub("BRCA", "BRCA ", paste(cancer, PAM50, sep = "")))

#sort 
data <- arrange(data, cancer_PAM50, TP53, RP3)

#remove infinite data
data <- filter(data, !is.infinite(RP3) & !is.infinite(miR34a))

#diploid only
data <- filter(data, abs(RP3_cna) < 0.1)

#rename TP53
data <- mutate(data, TP53 = if_else(TP53 == 1, "TP53mut", "TP53wt"))

#diploid only correlation analysis
#calculate correlation for all samples per cancer type
all <- data %>% 
  filter(RP3_cna < 0.1) %>%
  group_by(cancer) %>%
  summarize(
    n = n(),
    all_pvalue = signif(cor.test(RP3, miR34a, method = "spearman")$p.value, 3),
    all_R_estimate = signif(cor.test(RP3, miR34a, method = "spearman")$estimate, 3)
  )

#calculate correlation for p53 wt and mut samples per cancer type
p53 <- data %>%
  group_by(cancer, TP53) %>%
  filter(n() > 3) %>%
  summarize(
    n = n(),
    pvalue = signif(cor.test(RP3, miR34a, method = "spearman")$p.value, 3),
    R_estimate = signif(cor.test(RP3, miR34a, method = "spearman")$estimate, 3)
  ) %>%
  ungroup() %>%
  gather(metric, value, -(cancer:TP53)) %>%
  unite(temp, TP53, metric) %>%
  spread(temp, value)

full_join(all, p53, by = "cancer")
```
